ResultsNPS

### 2019-09-09 R/presentations/NPS_Work/presentation.Rmd
new changes on reports and corrected superquantiles.

---
title: "What I've been doing at NPS for three months"
author: "Franco Peschiera"
date: "MM, 2019"
output:
  slidy_presentation:
    css: ./../../../css/baobab_slidy.css
    incremental: yes
    footer: "ISAE-SUPAERO, Université de Toulouse, France"
    slide_level: 2
    toc: true
---

>>>>

---
title: "What I've been doing at NPS for three months"
author: "Franco Peschiera"
date: "Agusut, 2019"
output:
  slidy_presentation:
    css: ./../../../css/baobab_slidy.css
    incremental: yes
    footer: "ISAE-SUPAERO, Université de Toulouse, France"
    slide_level: 2
    toc: true
---

### 2019-09-09 R/scripts/resultsNPS.Rmd
new changes on reports and corrected superquantiles.

---
title: "ResultsNPS"
author: "Franco Peschiera"
date: "August 8, 2019"
output: html_document
editor_options: 
  chunk_output_type: console
params:
   size: medium
---

@@

import sys, os
opt_path = './'
opt_path = '../'
rel_path_python = '{}../python/'.format(opt_path)
path = os.path.join(r.current_dir, rel_path_python)
# print(path)
sys.path.insert(1, path)

@@

# This is read now as a paramer in the YAML (above).
# size = 'small'  # choose small, medium or large
df = compare_sto.get_instances[r.size]()
df = df.reset_index()

@@

```{r}
filtered_q_perf <- quality_perf %>% filter(between(dif_perc, -5, 5))
filtered_quant <- (1 - (filtered_q_perf %>% nrow)/ (quality_perf %>% nrow))*100
```
The following graph shows the distribution of relative gaps between the best integer solutions found in each of the two models. A negative relative gap means the `cuts` model outperformed the `base` model in that particular instance. Both extreme tails (`r filtered_quant %>% round(2)`\%̀) have been taken out to help better visualize it.

>>>>

---
title: "ResultsNPS"
author: "Franco Peschiera"
date: "August 8, 2019"
output:
  html_document: default
  pdf_document: default
params:
  size: medium
editor_options:
  chunk_output_type: console
---

@@

import sys, os
opt_path = './'
# opt_path = '../'
rel_path_python = '{}../python/'.format(opt_path)
path = os.path.join(r.current_dir, rel_path_python)
# print(path)
sys.path.insert(1, path)

@@

# This is read now as a paramer in the YAML (above).
# size = 'small'  # choose small, medium or large
# df = compare_sto.get_instances[r.size]()

################# manual alternative...
# exp_list = ['IT000125_20190808', 'IT000125_20190729']
# df = compare_sto.get_df_comparison(exp_list)
# df = df[df.scenario == 'numparalleltasks_2']

exp_list = ['IT000125_20190808', 'IT000125_20190812']
df = compare_sto.get_df_comparison(exp_list).reset_index()
# df = df[df.scenario == 'numparalleltasks_3']
df = df.query("scenario == 'numparalleltasks_3' or experiment==1")
################# manual alternative...

@@

```{r}
filtered_q_perf <- quality_perf %>% filter(between(dif_perc, -5, 5))
filtered_quant <- (1 - (filtered_q_perf %>% nrow)/ (quality_perf %>% nrow))*100
```
The following graph shows the distribution of relative gaps between the best integer solutions found in each of the two models. A negative relative gap means the `cuts` model outperformed the `base` model in that particular instance. Both extreme tails (`r filtered_quant %>% round(2)`\%) have been taken out to help better visualize it.
